Flexibility of interactions depends on habitat suitability

### 2019-09-11 paper/manuscript.Rmd
first paragraph of the discussion

>>>>

We found that environemntal stress, which we meassured using habitat suitability, was a very importat predictor for the number of partners a species interacts with. 
However, this relationship was highly variable among species. 
So much so that, at the population level, there is no discernable pattern between stress and the number of interacting species.
Interestingly, within species, there was a significant coorelaton between the number of partners a species has and the stress-partners relationship itself. 
Specifically, species with a large number of partners in low-stress communities, were more likely to have a negative relatiosnship and hence reduce the number of partners as stress increasses. 
Contrastingly, species in our datasets with a small number of parters in low-stress communities were more likely to have a larger number of partners in more stressful communities.
